---
title: "Homework 24"
format: html
editor: visual
---

## Overview

For your homework you will implement a data analysis using a dataset on crab growth measurements.

Set things up (hint: there is a new package to add with `library()`)

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(ggfortify)
```

## The data

Let's pull in some data appropriate biologists: crab measurements. This dataset includes measurements of farmed crabs.

```{r}
crabs <- read.csv(here("data","CrabAgePrediction.csv"))
glimpse(crabs)
```

One of the variables is categorical - let's fix that in the data.

```{r}
crabs$Sex<-as.factor(crabs$Sex)
```

## Question

Is there a relationship between height and weight in female crabs?

1.  Extract the data for just female crabs.

    ```{r}
    femcrab<-crabs|>
      group_by(Sex)|>
      filter(Sex=="F")
    ```

2.  Examine the response and predictor variables and use the flow chart from class to decide the appropriate statistical analysis (choose from: chi-square, 2-sample t-test or linear regression).

    ```{r}
    ggplot(femcrab, aes(Height, Weight))+
      geom_point()+
      ylab("Weight")+
      xlab("Height")
    ```

    Explain your answer here: I would say a simple linear regression is the most likely candidate because we are asking for the existence of a relation with both variable continuous.

3.  Work through the data analysis **following all of the steps provided in chapter 5 of your book**. You may use class notes or homework keys as a guide.

```{r}
modelhw<-lm(Weight~Height, data = femcrab)
```

Using the model:

```{r}
autoplot(modelhw, smooth.colour = NA)
```

carrying out the test:

```{r}
anova(modelhw)
```

```{r}
summary(modelhw)
```

BAck to the plot:

```{r}
ggplot(femcrab, aes(Height, Weight))+
  geom_point()+
  geom_smooth(method = 'lm')+
  ylab("Weight")+
  xlab("Height")+
  theme_bw()
```

There does seem to be some strong positive correlation between Height and Weight of female crabs.
