---
title: "Biostats - Homework 20"
format: html
editor: visual
---

### Introduction

The objective of this assignment is to have you continue practicing the skills you have learned in Chapters 3 and 4 of Getting Started with R and reinforce the ideas we discussed in class regarding the Weissgerber et al. paper. Please complete all of the following steps:

1.  Write the code to set up your workspace.

```{r}
rm(list = ls())
library(here)
library(tidyverse)
```

2.  Read in the dataset called soil_data.csv and name it "soil."

```{r}
soil<-read.csv(here("data","soil_data.csv"))
```

3.  Create a histogram for the SOM_percent column in the dataframe. Accept the default number of bins.

```{r}
ggplot(soil, aes(SOM_percent))+
  geom_histogram()
```

How would you describe the mean_SOM data based on viewing the histogram? Write your answer below:

I would first think the mean would be somewhere around the 5-7 range, maybe closer to 7 because of the rightward skew.

4.  Create a new dataframe called SOM by calculating for each forest the mean soil organic matter and the standard deviation of soil organic matter. Make sure to name variables you create "mean_SOM" and "sd_SOM" so that the next code chunk I give you works.

```{r}
SOM<- soil|>
  group_by(Forest)|>
  mutate(mean_SOM=mean(SOM_percent))|>
  mutate(sd_SOM=sd(SOM_percent))
```

5.  Now run the following code chunk which will create a bar plot of mean soil organic matter per forest, with standard deviation as error bars.

```{r}
ggplot(SOM, aes(Forest, mean_SOM))+
  geom_errorbar(aes(ymax = mean_SOM + sd_SOM, ymin = mean_SOM - sd_SOM), width = 0.2)+
  geom_col(fill = "white", color = "black")+
  ylab("Mean percent soil organic matter")+
  xlab("Forest name")
```

Based on what you see in the bar chart, how would you describe the pattern of SOM between the 4 different forests? Write your answer here:

I really don't know what I am looking at here... It looks like maybe the size of each subsection of the bars would indicate the differences in SOM, so I would guess Degrasse has the lowest and Kip has the highest on average.

Now create a boxplot of the SOM_percent data. Use Forest as the x-axis variable and overlay the point data on top of the boxplot. Make the points blue and somewhat transparent. Call the x-axis "Forest name" and the y-axis "Percent soil organic matter" (hint: See homework 18...).

```{r}
ggplot(soil, aes(Forest, SOM_percent))+
  geom_boxplot()+
  geom_point(size=2, colour='blue',alpha=.5)+
  xlab("Forest name")+
  ylab("Percent soil organic matter")

```

Based on what you see in the box plot, write out your answers the following questions:

-   how would you describe the pattern of SOM between the 4 different forests?

Degrasse seems to be significantly lower in percent cover, Donnerville and South Hammond seem to be fairly even, and Kip seems to be significantly more than all, but could be even with the prior two after further statistical tests.

-   What do you notice that is different from how the data were displayed in the bar plot?

This was much easier to understand. I don't know if my bar plot was done correctly, but if it was, it didn't really make sense. The box plot gives me a good visual of the spread of the data, but the bar plot was hard to even just look at.

-   Which plot type is more informative? Explain your answer.

By far, the box plots. I am able to see the quartiles, any outliers, as well as simply how spread apart the data are. The bar plot did not really give me much information at all.
